### 2022-10-30 doc/src/MSLevel.tex
Major interrupt numbers 64 and above are possible as custom interrupts
Signed-off-by: John Hauser <31252952+jhauser-us@users.noreply.github.com>

@@

It is expected that many systems will forego
priority configurability of major interrupts and simply
have the\/ \z{iprio} array be all read-only zeros.
Systems that need this priority configurability can try
to arrange for each hart's external interrupt controller
to be relatively close to the hart, by, for example, limiting
the system to at most a few small cores connected to an APLIC,
or alternatively by giving every hart its own IMSIC.

\end{commentary}

>>>>

\begin{commentary}
While many of the standard registers such as\/ \z{mip}/\z{miph}
and\/ \z{mie}/\z{mieh} have space for major interrupts
only in the range 0--63, custom interrupts with numbers
64 and above are conceivable with added custom support.
CSRs\/ \z{mtopi} (Section~\ref{sec:mtopi})
and\/ \z{stopi} (Section~\ref{sec:stopi}) allow for
major interrupt numbers potentially as large as 4095.
\end{commentary}

@@

It is expected that many systems will forego
priority configurability of major interrupts and simply
have the\/ \z{iprio} array be all read-only zeros.
Systems that need this priority configurability can try
to arrange for each hart's external interrupt controller
to be relatively close to the hart, by, for example, limiting
the system to at most a few small cores connected to an APLIC,
or alternatively by giving every hart its own IMSIC.
\end{commentary}
